\documentclass[9pt]{extarticle}
\usepackage{resume}


%%%%%%%%%%%%%%%%%%%% Credit %%%%%%%%%%%%%%%%%%%%
\usepackage[pdftex,
            pdfauthor={Tsion Behailu},
            pdftitle={Tsion Behailu - Resume},
            pdfsubject={Tsion Behailu - Resume},
            pdfkeywords={tsion, behailu, resume},
            pdfproducer={Created using LaTex},
            pdfcreator={pdflatex}]{hyperref}
\sffamily            
\usepackage{hyperref}

\begin{document}
%%%%%%%%%%%%%%%%%%%% Title %%%%%%%%%%%%%%%%%%%%%%%%%%

% \name{\textbf{TSION BEHAILU}}
% {\url{www.tsion.me}}
% {tsionbehailu@gmail.com $\bullet$ 404.944.5352}

\name{TSION BEHAILU}{www.tsion.me}{tsionbehailu@gmail.com $\bullet$ 404.944.5352}

\vspace
%%%%%%%%%%%%%%%%%%%% Education %%%%%%%%%%%%%%%%%%%%%%
\header{Education}

\begin{body}
\vspace{1pt}

\school{University of California, Berkeley}{August 2011 - May 2015}{Major: Computer Science}

\end{body}


%%%%%%%%%%%%%%%%%%%%% Skills %%%%%%%%%%%%%%%%%%%%%%%
\vspace*{-4pt}
\header{Skills}

\begin{body}
  \begin{itemize}
  \itemsep -2pt
  \item Java, Ruby, C, Python, Matlab, \LaTeX, AutoCAD
  \item Eclipse, Teradata, Ruby on Rails, Coda, XCode, Hadoop, Logism
  \end{itemize}
\end{body}

\vspace*{-4pt}
%%%%%%%%%%%%%%%%%%%%% Experience %%%%%%%%%%%%%%%%%%%%%%
\header{Experience}
\begin{body}
\vspace{2pt}
\jobentry{Software Engineering Intern}{Groupon, Palo Alto, CA}{June 2014 - August 2014}{Automated the collection of page performance metrics for the SEO team. Wrote clients for various external API’s, such as Dotcom-Monitor and Pingdom, to collect the performance statistics of SEO pages and integrated these into a rails application. Scheduled cron jobs regularly pull the page performance data to a MySQL database, and then add the data to Teradata. Application was deployed to production and is now accessible to all Groupon teams.}

\jobentry{Research Assistant/Marketing Director}{Institute for Law and Policy Planning, Berkeley, CA}{October 2011 - Present}{Shaped the marketing structure of ILPP to produce better results in both news searches and RFPs, ultimately leading to more jobs for the organization. }

    
\end{body}

\vspace*{-4pt}
%%%%%%%%%%%%%%%%%%%%%%%% Projects %%%%%%%%%%%%%%%%%%%%%%%%
\header{Projects}
\begin{body}
\vspace{1pt}

% ICT Research
\research{Information Communications Technologies (ICT) Development for Sub-Saharan Farmers}{August 2014 - Present}{www.tsionbehailu.me/research}{Advisor: Prof. Tapan Parikh, School of Information}{Designing ICTs to Increase Smallholder Farmers' Access to Markets and Knowledge. Identify needs and defines opportunities through innovative ICT-based applications and systems which can increase agricultural small-holder productivity, profitability, and sustainability}{Funded by NSF, CRA-W, CDC}

% \textbf {Information Communications Technologies (ICT) Development for Sub-Saharan Farmers} 
% %\emph{Berkeley,CA} 
% \hfill 
% \emph{August 2014 - Present}
% \url{www.tsionbehailu.me/research}
% \vspace*{-4pt}
% \begin{itemize}
%   \itemsep -2pt
%   \item[] Advisor: Prof. Tapan Parikh, School of Information
%   \item Designing ICTs to Increase Smallholder Farmers' Access to Markets and Knowledge. Identify needs and defines opportunities through innovative ICT-based applications and systems which can increase agricultural small-holder productivity, profitability, and sustainability
%    \item Funded by NSF, CRA-W, CDC
% \end{itemize}

\vspace*{-1pt}

\projectnolink{TLS Handshake}{November 2014}{Implemented own version of the SSL handshake, appropriately named the TLS (Terribly Lacking Security) handshake. Establishes a handshake with the provided server and can send messages to the server by typing into the terminal.}


% MULTI-AGENT PACMAN
% https://github.com/tbehailu/multi-agent-pacman.git

\projectnolink{Pacman Search \& Multi-Agent Pacman}{February 2014}{Built general search algorithms and applied them to pacman agent to find paths through a maze. Designed additional agents for game, implementing both minimax and expectimax search.}

% Processor Design
% \project{Processor Design}{November 2013}{https://github.com/tbehailu/Processor.git}{Used Logisim to create a 16-bit two-cycle processor. Designed the processor's register file to manage the four 16-bit registers in the Instruction Set Architecture (ISA) and the ALU to do a total of ten operations. Built the Data Memory using a built-in Logism RAM module. Wrote two MIPS functions for additional testing of the final CPU design.}
   
   
% Best Regards
\project{BestRegards.co: Handwritten Thank You Cards Generator}{October 2013 - Present}{https://github.com/tbehailu/best_regards_v2}{Co-founded a web service that automates handwritten thank you cards using Ruby on Rails. Built an ecommerce platform and integrated Stripe's API to accept payments.}
            
% Bird Bounce
\project{Bird Bounce: An iOS Mobile Game}{October 2013 - Present}{https://github.com/tbehailu/BirdBounce}{Developed an iOS mobile game with a partner on Kobold2D, a 2D game framework. All graphics were done using Adobe Illustrator.}

% \project{The Beauty of Knotted Sculptures}{August 2013 - December 2013}{https://github.com/tbehailu/knots.git}{Analyzed and deformed selected knots from knot table into 2D diagrams in order to find symmetry and create 3D model with the use of AutoCAD as a research apprentice.}
% Advisor: Prof. Carlo Sequin, Electrical Engineering \& Computer Science Department


\end{body}

\vspace*{-4pt}
%%%%%%%%%%%%%%%%%%%%%%% Coursework %%%%%%%%%%%%%%%%%%%%%%%
\header{Coursework}

\begin{body}
\vspace{-8pt}
\coursework{Internet Architecture}{Computer Security}{Artificial Intelligence}{Machine Learning} {Data Structures (\emph{Java})}{Discrete Math \& Probability Theory}{Economic Theory--Micro}{Technology Entrepreneurship}{Finance}
\end{body}

% Artificial Intelligence
% Machine Learning
% Data Structures \& Programming Methodology (\emph{Java})
% The Structure and Interpretation of Computer Programs (\emph{Python/Scheme})
% --- Introduction to Computer Programming for Scientists and Engineers (\emph{Matlab})
% --- Self-Paced C for Programmers (\emph{C Programming Language})
% --- Multivariable Calculus

% --- Introduction to Digital Electronics
% --- Discrete Mathematics \& Probability Theory
% --- Introduction to Design and Analysis (\emph{Autodesk Inventor 3D CAD Software})
% --- The Structure \& Properties of Civil Engineering Materials
% --- Physics for Scientists \& Engineers
% --- iOS Game Development DeCal
% Economic Theory--Micro
% Technology Entrepreneurship
% Introduction to Finance

\vspace{-8pt}
%%%%%%%%%%%%%%%%%% Activities %%%%%%%%%%%%%%%%%%%%%
\header{Activities}

\begin{body}

\activitynorole{Square College Code Camp}{January 2014}{One of twenty female CS students chosen from the U.S. and Canada to participate in a four-day immersion program at Square HQ. Completed workshops in CSS architecture, iOS Development, and Security Engineering.}

\activity{Winter Academic Training Camp (WAT Camp)}{Computer Science Instructor}{January 15-19, 2014}{www.tsion.me/wat-camp-2014}{Instructor for \emph{CS61A: Structure and Interpretation of Computer Programs} at WAT Camp. Covered elements of programming, lambda functions, environment diagrams, sequences, objects and classes, and more. Course was conducted in Python.}

\activitynolink{Undergraduate Study Committee}{L\&S Computer Science Representative}{September 2013 - Present}{ Aid in the making of departmental decisions with the Computer Science Department faculty and staff as a representative for Letters \& Science Computer Science students.}

\activitysimple{Cal N.E.R.D.S.}{Researcher for Cal New Experiences for Research \& Diversity in Science}{March 2013 - Present}

\end{body}

\end{document}